Keep your Laziness in Check

### 2018-03-05 paper/main.tex
[paper] some work on section 3

@@

>>>>

There is a general pattern between a type \lk{a} and
its \textit{demand type}, for which we will write \lk{Demand a} from
now on. In both the example on lists and the example on maps,
a \lk{Thunk} type constructor is placed around all of the constructor
arguments to the original type. The \lk{Thunk} type has the following
definition:
\begin{inlinecode}
data Thunk a = E !a | T
\end{inlinecode}
Its two constructors \lk{E} and \lk{T} represents an evaluated
fragment of the original data, and unexplored regions of the original
data, respectively.

This design is motivated by the runtime representation of Haskell
values. Boxed values in Haskell are indirectly represented by a
pointer, and the pointer can lead to either a constructor with
pointers to deeper parts of the value, or a piece of unevaluated code,
which will produce a fragment of the value when evaluated. This piece
of code is also know as a thunk.

The \lk{Thunk} type reifies \hzh{there is a slight caveat here though,
we don't really capture sharing with this representation} the runtime
representation into a Haskell value. Programmers can then inspect
these demand values within Haskell. Most importantly, the demand types
form the vocabulary of specifications on laziness.

A \textit{specification} in StrictCheck is a function that computes
demand values. When we talk about Haskell function's laziness
informally, we often refer to these functions as ``strict'' or
``lazy'' in its arguments. There is a lot of information we can unpack
from such phrases --- how strict the function is in its arguments, the
dependency of the strictness on the argument values, and the
relationship between demand on inputs with demand on the output.

StrictCheck specifications allows programmers to convey these
information accurately. A specification takes a demand on the output,
all of the inputs to the specified function, and computes a demand on
all the inputs. For example, the specification of the \lk{take}
function will have type \lk{Demand [a] -> Int -> [a] -> (Demand Int,
Demand [a])}.

\hzh{I want to say something about why we chose this design, but I'm not
actually sure why...}

The translation between a data type to its demand type and between a
function type to its specification type are mechanic, and although we
have presented them in a way that involves creating new demand type
definitions, our implementation handles all of this automatically
through generic programming. We delay this discussion
to \Cref{sec:generic-programming}.

@@

\section{Generic Programming}
\label{sec:generic-programming}
